Pollution, agricultural productivity, and development: Evidence from coal in plants in India\footnote{All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}

### 2023-02-11 draft/draft.tex
updating tables

  pdftitle={Pollution, agricultural productivity, and development: Evidence from coal in plants in India},

@@

\title{Pollution, agricultural productivity, and development: Evidence from coal in plants in India\footnote{I thank Marc Bellemare and David Sungho Park for comments and suggestions that greatly improved the quality of the paper. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-01-20}

@@

While I am not able to explicitly test effects on land productivity, I look at how adults allocate labor over the last seven days using the National Sample Survey and creating a district-level exposure measure based on the timing of the survey for each household. An additional day of wind over the previous week decreases overall labor allocation by 0.027 days. However, the overall results show stark heterogeneity based on age; the older half of the sample greatly decreases labor allocation in response to pollution exposure while the younger half increases overall labor allocation. Older adults decrease labor allocation to both farm and non-farm labor, while younger adults increase labor allocated to farm labor. This is suggestive evidence of productivity effects being driven by the health and productivity effects on individuals, since older adults are more susceptible to pollution and they also greatly decrease non-farm employment, which presumably will no suffer any possible direct effects of pollution on productivity. The preponderance of results seems to indicate that effects on labor are the most likely mechanism.

@@

\caption{\label{tab:yieldtable}Wind direction and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{all} & \multicolumn{1}{c}{monsoon} & \multicolumn{1}{c}{winter} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
wind & -0.003*** & -0.003*** & -0.0007*** & -0.002*** & -0.004***\\
 & (0.0002) & (0.0002) & (9.24e-5) & (0.0002) & (0.0003)\\
rain (z) &  & 0.029*** & 0.008*** & 0.075*** & 0.006***\\
 &  & (0.0004) & (0.001) & (0.002) & (0.0005)\\
mean temp (10s) &  & -0.0004*** & -0.007*** & -0.002*** & -0.008***\\
 &  & (5.53e-5) & (0.0004) & (0.0001) & (9.83e-5)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & No & No\\
year & Yes & Yes & No & Yes & Yes\\
district-year-season & No & No & Yes & No & No\\
village & No & No & No & Yes & Yes\\
\midrule
observations & 2,387,417 & 2,371,221 & 2,371,221 & 1,256,951 & 1,114,270\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablepm}Particulate matter (PM 2.5) and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{all} & \multicolumn{1}{c}{monsoon} & \multicolumn{1}{c}{winter} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
particulate matter & 0.0000 & 0.0005*** & -0.0004*** & 0.002*** & 0.0004***\\
(PM 2.5, '000s) & (0.0000) & (3.17e-5) & (5.72e-5) & (9.87e-5) & (3.7e-5)\\
rain (z) &  & 0.030*** & 0.008*** & 0.075*** & 0.007***\\
 &  & (0.0004) & (0.001) & (0.002) & (0.0005)\\
mean temp (10s) &  & -0.0003*** & -0.007*** & -0.002*** & -0.008***\\
 &  & (5.63e-5) & (0.0004) & (0.0001) & (9.79e-5)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & No & No\\
year & Yes & Yes & No & Yes & Yes\\
district-year-season & No & No & Yes & No & No\\
village & No & No & No & Yes & Yes\\
\midrule
observations & 2,387,417 & 2,371,221 & 2,371,221 & 1,256,951 & 1,114,270\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtabletwo}Pollution and agricultural productivity, IV estimates}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{all} & \multicolumn{1}{c}{monsoon} & \multicolumn{1}{c}{winter} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
particulate matter & -0.021*** & -0.024*** & -0.032*** & -0.012*** & -0.035***\\
(PM 2.5) & (0.001) & (0.002) & (0.005) & (0.001) & (0.003)\\
rain (z) &  & -0.011*** & -4.24e-5 & 0.078*** & -0.042***\\
 &  & (0.003) & (0.002) & (0.002) & (0.004)\\
mean temp (10s) &  & -0.005*** & -0.007*** & -0.002*** & -0.008***\\
 &  & (0.0003) & (0.0004) & (0.0001) & (0.0001)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & No & No\\
year & Yes & Yes & No & Yes & Yes\\
district-year-season & No & No & Yes & No & No\\
village & No & No & No & Yes & Yes\\
\midrule
observations & 2,387,417 & 2,371,221 & 2,371,221 & 1,256,951 & 1,114,270\\
\midrule
\textbf{first stage:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
wind & 0.145*** & 0.111*** & 0.022*** & 0.157*** & 0.105***\\
 & (0.002) & (0.002) & (0.002) & (0.002) & (0.004)\\
rain (z) &  & -1.68*** & -0.239*** & 0.225*** & -1.37***\\
 &  & (0.011) & (0.017) & (0.015) & (0.010)\\
mean temp (10s) &  & -0.192*** & 0.002 & -0.021*** & -0.007***\\
 &  & (0.0009) & (0.004) & (0.001) & (0.002)\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablehet}Heterogeneity in the effects of pollution on productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{>p(50)} & \multicolumn{1}{c}{<=p(50)} & \multicolumn{3}{c}{all} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
wind & -0.003*** & -0.033*** & -0.004*** & 0.0006 & 0.000\\
 & (0.0002) & (0.002) & (0.0003) & (0.0005) & (0.001)\\
rain (z) & 0.028*** & 0.032*** & 0.028*** & 0.028*** & 0.028***\\
 & (0.0006) & (0.0005) & (0.0004) & (0.0004) & (0.0004)\\
mean temp (10s) & -0.001*** & 0.0006*** & -0.0004*** & -0.0004*** & -0.0004***\\
 & (7.66e-5) & (7.9e-5) & (5.55e-5) & (5.56e-5) & (5.49e-5)\\
wind x rain &  &  & 0.0005*** &  & \\
 &  &  & (6.74e-5) &  & \\
wind squared &  &  &  & -0.0002*** & \\
 &  &  &  & (3.58e-5) & \\
wind x starting yield &  &  &  &  & -0.001**\\
 &  &  &  &  & (0.0006)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes & Yes\\
\midrule
observations & 1,112,082 & 1,259,139 & 2,371,221 & 2,371,221 & 2,367,248\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:labortable}Wind direction and labor allocation}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}}
\toprule
  & all & all & self & wage & farm & non-farm\\
\midrule
wind & -0.021 & -0.027* & 0.008 & -0.034** & 0.035* & -0.061**\\
 & (0.015) & (0.015) & (0.017) & (0.016) & (0.019) & (0.025)\\
controls & No & Yes & Yes & Yes & Yes & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
district & Yes & Yes & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes & Yes & Yes\\
\textbf{varying slopes:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
year (by district) & Yes & Yes & Yes & Yes & Yes & Yes\\
\midrule
observations & 899,045 & 898,856 & 898,856 & 898,856 & 898,856 & 898,856\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:labortableold}Wind direction and labor allocation, heterogeneity by age}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}}
\toprule
  & all & self & wage & farm & non-farm\\
\midrule
wind & 0.061*** & 0.096*** & -0.034 & 0.068*** & -0.006\\
 & (0.023) & (0.022) & (0.024) & (0.020) & (0.030)\\
wind times age>=38 & -0.207*** & -0.207*** & -0.0001 & -0.078*** & -0.129***\\
 & (0.037) & (0.033) & (0.040) & (0.020) & (0.030)\\
controls & Yes & Yes & Yes & Yes & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
district & Yes & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes & Yes\\
\textbf{varying slopes:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
year (by district) & Yes & Yes & Yes & Yes & Yes\\
\midrule
observations & 898,856 & 898,856 & 898,856 & 898,856 & 898,856\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:ntltable}Wind direction and nightlight growth}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2)\\
\midrule
wind (lagged) & -0.080*** & -0.083***\\
 & (0.015) & (0.015)\\
rain (z, lagged) &  & -0.035***\\
 &  & (0.002)\\
\textbf{fixed effects:} & \textbf{} & \textbf{}\\
village & Yes & Yes\\
year & Yes & Yes\\
\textbf{varying slopes:} & \textbf{} & \textbf{}\\
year (by village) & Yes & Yes\\
\midrule
observations & 2,146,715 & 2,146,715\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\setcounter{table}{0} \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}} 
\FloatBarrier

@@

\FloatBarrier
\newpage
\begin{table}[H]

\caption{\label{tab:yieldtablepostplant}Wind direction and agricultural productivity, post-coal plant only}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{all} & \multicolumn{1}{c}{monsoon} & \multicolumn{1}{c}{winter} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
wind & -0.003*** & -0.002*** & -0.0006*** & -0.002*** & -0.003***\\
 & (0.0002) & (0.0002) & (9.56e-5) & (0.0002) & (0.0003)\\
rain (z) &  & 0.018*** & 0.008*** & 0.061*** & 0.003***\\
 &  & (0.0005) & (0.001) & (0.002) & (0.0005)\\
mean temp (10s) &  & 0.0008*** & -0.005*** & 0.005*** & -0.008***\\
 &  & (5.28e-5) & (0.0004) & (0.0001) & (0.0001)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & No & No\\
year & Yes & Yes & No & Yes & Yes\\
district-year-season & No & No & Yes & No & No\\
village & No & No & No & Yes & Yes\\
\midrule
observations & 1,886,956 & 1,872,177 & 1,872,177 & 996,509 & 875,668\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The sample is restricted to village-years after a coal plant was built near the village. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

\FloatBarrier
\newpage
\begin{table}

>>>>

  pdftitle={Pollution, agricultural productivity, and development: Evidence from coal plants in India},

@@

\title{Pollution, agricultural productivity, and development: Evidence from coal plants in India\footnote{I thank Marc Bellemare and David Sungho Park for comments and suggestions that greatly improved the quality of the paper. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-02-10}

@@

While I am not able to explicitly test effects on land productivity, I look at how adults allocate labor over the last seven days using the National Sample Survey and creating a district-level exposure measure based on the timing of the survey for each household. An additional day of wind over the previous week decreases overall labor allocation by 0.055 days. However, the overall results show stark heterogeneity based on age; the older half of the sample greatly decreases labor allocation in response to pollution exposure while the younger half increases overall labor allocation. Older adults decrease labor allocation to both farm and non-farm labor, while younger adults increase labor allocated to farm labor. This is suggestive evidence of productivity effects being driven by the health and productivity effects on individuals, since older adults are more susceptible to pollution and they also greatly decrease non-farm employment, which presumably will no suffer any possible direct effects of pollution on productivity. The preponderance of results seems to indicate that effects on labor are the most likely mechanism.

@@

\caption{\label{tab:yieldtable}Wind direction and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{all} & \multicolumn{1}{c}{monsoon} & \multicolumn{1}{c}{winter} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
wind & -0.003*** & -0.003*** & -0.0007*** & -0.002*** & -0.004***\\
 & (0.0002) & (0.0002) & (9.24e-5) & (0.0002) & (0.0003)\\
rain (z) &  & 0.029*** & 0.008*** & 0.075*** & 0.006***\\
 &  & (0.0004) & (0.001) & (0.002) & (0.0005)\\
mean temp (10s) &  & -0.0004*** & -0.007*** & -0.002*** & -0.008***\\
 &  & (5.53e-5) & (0.0004) & (0.0001) & (9.83e-5)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & No & No\\
year & Yes & Yes & No & Yes & Yes\\
district-year-season & No & No & Yes & No & No\\
village & No & No & No & Yes & Yes\\
\midrule
observations & 2,387,417 & 2,371,221 & 2,371,221 & 1,256,951 & 1,114,270\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablepm}Particulate matter (PM 2.5) and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{all} & \multicolumn{1}{c}{monsoon} & \multicolumn{1}{c}{winter} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
particulate matter & 0.0000 & 0.0005*** & -0.0004*** & 0.002*** & 0.0004***\\
(PM 2.5, '000s) & (0.0000) & (3.17e-5) & (5.72e-5) & (9.87e-5) & (3.7e-5)\\
rain (z) &  & 0.030*** & 0.008*** & 0.075*** & 0.007***\\
 &  & (0.0004) & (0.001) & (0.002) & (0.0005)\\
mean temp (10s) &  & -0.0003*** & -0.007*** & -0.002*** & -0.008***\\
 &  & (5.63e-5) & (0.0004) & (0.0001) & (9.79e-5)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & No & No\\
year & Yes & Yes & No & Yes & Yes\\
district-year-season & No & No & Yes & No & No\\
village & No & No & No & Yes & Yes\\
\midrule
observations & 2,387,417 & 2,371,221 & 2,371,221 & 1,256,951 & 1,114,270\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtabletwo}Pollution and agricultural productivity, IV estimates}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{all} & \multicolumn{1}{c}{monsoon} & \multicolumn{1}{c}{winter} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
particulate matter & -0.021*** & -0.024*** & -0.032*** & -0.012*** & -0.035***\\
(PM 2.5) & (0.001) & (0.002) & (0.005) & (0.001) & (0.003)\\
rain (z) &  & -0.011*** & -4.24e-5 & 0.078*** & -0.042***\\
 &  & (0.003) & (0.002) & (0.002) & (0.004)\\
mean temp (10s) &  & -0.005*** & -0.007*** & -0.002*** & -0.008***\\
 &  & (0.0003) & (0.0004) & (0.0001) & (0.0001)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & No & No\\
year & Yes & Yes & No & Yes & Yes\\
district-year-season & No & No & Yes & No & No\\
village & No & No & No & Yes & Yes\\
\midrule
observations & 2,387,417 & 2,371,221 & 2,371,221 & 1,256,951 & 1,114,270\\
\midrule
\textbf{first stage:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
wind & 0.145*** & 0.111*** & 0.022*** & 0.157*** & 0.105***\\
 & (0.002) & (0.002) & (0.002) & (0.002) & (0.004)\\
rain (z) &  & -1.68*** & -0.239*** & 0.225*** & -1.37***\\
 &  & (0.011) & (0.017) & (0.015) & (0.010)\\
mean temp (10s) &  & -0.192*** & 0.002 & -0.021*** & -0.007***\\
 &  & (0.0009) & (0.004) & (0.001) & (0.002)\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablehet}Heterogeneity in the effects of pollution on productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{>p(50)} & \multicolumn{1}{c}{<=p(50)} & \multicolumn{3}{c}{all} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
wind & -0.003*** & -0.033*** & -0.004*** & 0.0006 & 0.000\\
 & (0.0002) & (0.002) & (0.0003) & (0.0005) & (0.001)\\
rain (z) & 0.028*** & 0.032*** & 0.028*** & 0.028*** & 0.028***\\
 & (0.0006) & (0.0005) & (0.0004) & (0.0004) & (0.0004)\\
mean temp (10s) & -0.001*** & 0.0006*** & -0.0004*** & -0.0004*** & -0.0004***\\
 & (7.66e-5) & (7.9e-5) & (5.55e-5) & (5.56e-5) & (5.49e-5)\\
wind x rain &  &  & 0.0005*** &  & \\
 &  &  & (6.74e-5) &  & \\
wind squared &  &  &  & -0.0002*** & \\
 &  &  &  & (3.58e-5) & \\
wind x starting yield &  &  &  &  & -0.001**\\
 &  &  &  &  & (0.0006)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes & Yes\\
\midrule
observations & 1,112,082 & 1,259,139 & 2,371,221 & 2,371,221 & 2,367,248\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the *maximum* observed exposure. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:labortablerural}Wind direction and labor allocation, rural only}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{1.5cm}}
\toprule
  & all & all & self & wage & farm & non-farm\\
\midrule
\textbf{rural} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
wind & -0.112*** & -0.118*** & -0.050* & -0.068** & -0.002 & -0.116***\\
 & (0.036) & (0.029) & (0.030) & (0.031) & (0.028) & (0.034)\\
DV mean & 3.499 & 3.499 & 2.172 & 1.327 & 1.260 & 2.240\\
observations & 529,562 & 529,466 & 529,466 & 529,466 & 529,466 & 529,466\\
\midrule
\textbf{urban} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
wind & -0.020 & -0.030 & -0.011 & -0.019 & 0.023* & -0.053\\
 & (0.033) & (0.041) & (0.039) & (0.031) & (0.014) & (0.048)\\
DV mean & 3.040 & 3.040 & 1.393 & 1.647 & 0.101 & 2.939\\
observations & 369,483 & 369,390 & 369,390 & 369,390 & 369,390 & 369,390\\
\midrule
controls & No & Yes & Yes & Yes & Yes & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
district & Yes & Yes & Yes & Yes & Yes & Yes\\
state-month & Yes & Yes & Yes & Yes & Yes & Yes\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the district level. Control variables include female, age, age squared, and (years of) education. The outcome in each regression is days worked in the previous seven days. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

@@

\caption{\label{tab:ntltable}Wind direction and nightlight growth}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
wind (lag) & -0.024*** & -0.024*** &  & \\
 & (0.003) & (0.003) &  & \\
wind (lead) &  &  & -0.001 & -0.001\\
 &  &  & (0.002) & (0.002)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes\\
\textbf{varying slopes:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
year (by village) & Yes & Yes & Yes & Yes\\
\midrule
observations & 1,694,535 & 1,694,535 & 1,807,504 & 1,807,504\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is logged nightlights. Rainfall is included in columns (2) and (4). * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\beginappendix
\FloatBarrier

@@

\caption{\label{tab:yieldtablepostplant}Wind direction and agricultural productivity, post-coal plant only}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{all} & \multicolumn{1}{c}{monsoon} & \multicolumn{1}{c}{winter} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
  & (1) & (2) & (3) & (4) & (5)\\
\midrule
wind & -0.003*** & -0.002*** & -0.0006*** & -0.002*** & -0.003***\\
 & (0.0002) & (0.0002) & (9.56e-5) & (0.0002) & (0.0003)\\
rain (z) &  & 0.018*** & 0.008*** & 0.061*** & 0.003***\\
 &  & (0.0005) & (0.001) & (0.002) & (0.0005)\\
mean temp (10s) &  & 0.0008*** & -0.005*** & 0.005*** & -0.008***\\
 &  & (5.28e-5) & (0.0004) & (0.0001) & (0.0001)\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village-season & Yes & Yes & Yes & No & No\\
year & Yes & Yes & No & Yes & Yes\\
district-year-season & No & No & Yes & No & No\\
village & No & No & No & Yes & Yes\\
\midrule
observations & 1,886,956 & 1,872,177 & 1,872,177 & 996,509 & 875,668\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The sample is restricted to village-years after a coal plant was built near the village. The outcome in all regressions estimated agricultural yield (tons per hectare). * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}
